---
output: github_document
editor_options: 
  chunk_output_type: console
---


[![Travis-CI Build Status](https://travis-ci.org/mdsumner/tasmapr.svg?branch=master)](https://travis-ci.org/mdsumner/tasmapr)



# tasmapr

The goal of tasmapr is to provide background maps of Tasmania for R leaflet. 

# Install

```{r, eval=FALSE}
devtools::install_github("mdsumner/tasmapr")
```
## Example

This is a basic example which shows you how to make an awesome map!



```{r example, eval = FALSE}
library(tasmapr)
tasmap()  ## Topographic basemap


tasmap(basemap = "TTSA")  ## Tasmania Towns Street Atlas

tasmap(basemap = "HillshadeGrey")  ## hill shade

```

See it here: http://rpubs.com/cyclemumner/283273


See https://github.com/mdsumner/wmts.git for a way to get these layers as raster data. 

## Code of Conduct
  
Please note that the tasmapr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/1/0/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

